---
title: "Hmeta_drugs"
output: html_document
date: "2023-02-09"
---

```{r}
library(tidyverse)
library(magrittr)
library(reshape2)
library(coda)
library(lattice)
library(broom)
library(ggpubr)
library(ggmcmc)
library(gghalves)
library(R.matlab)
library("readxl")
library(dplyr)
library(ggplot2)
library(gridExtra)
library(rjags)
library(readr)
library(tidyr)
library(cowplot)
source("/Users/sershadmanesh/Nextcloud/Drug_study/Public/HMeta-d-master-Fleming,S/R/trials2counts.R")
source("/Users/sershadmanesh/Nextcloud/Drug_study/Public/HMeta-d-master-Fleming,S/R/fit_metad_groupcorr.R")
source("/Users/sershadmanesh/Nextcloud/Drug_study/Public/accessory/permute_meta_drugs_beforefit_accessor.R")
source("/Users/sershadmanesh/Nextcloud/Drug_study/Public/plot/compare_mbmf_reg_plot.R")

```
# just for better visualization of plots
```{r}
thsara =theme(axis.title.y = element_text(hjust = 0.5, size = 16),
          axis.title.x = element_text(size = 16),
          axis.text = element_text(size = 14),
            axis.line = element_line(colour = "black"),
            panel.border = element_blank(),
            panel.grid = element_blank(),
            panel.background = element_blank(),
            legend.position = "right",
            legend.background=element_blank()
      )
```

#The data from perceptual task was read and fitted according to Hmeta package from Fleming,S.
```{r}
ndrug = 3
nt_bl =25
nsub = 30
nblk = 8
nRatings = 6
nrat= 2*6 # we have 2 response for choice
drug = readRDS("/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/drug.rds") # order of drug days for each subject
adressdrug = "/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/main_data/complete/" # data from perceptual tasks
completesubs = c(102:112, 114:117, 119:133) 

nrg_s1 = list()
nrg_s2 = list()
for (dru in 1:ndrug){
  ns1=matrix(0,nrow =nrat,ncol = nsub )
  ns2=matrix(0,nrow =nrat,ncol = nsub )
  for(sub in 1:nsub){
    subid = completesubs[sub]
    drugpos = drug[sub,dru]
    data = readMat(paste0(adressdrug,subid,"/","perceptData",subid,"-",drugpos,".mat"))
    response = c()
    rating = c()
    stimID = c()
    for (blk in 1:nblk){
      adress_subj = data$DATA[,,blk]$results[,,1]
      response = c(response, adress_subj$response)
      rating = c(rating, adress_subj$responseConf)
      rating[rating==0]= mean(rating[rating!=0]) # putting the average confidence for trials that there was no response.
      rating  = floor((rating-50)*((nRatings-1)/50) + 1)
      stimID_subj = rep(0,nt_bl)
      stimID_subj[adress_subj$correct==1]= adress_subj$response[adress_subj$correct==1]
      wrongres = adress_subj$response[adress_subj$correct==0]
      stimID_subj[adress_subj$correct==0]= (wrongres%%2)+1
      stimID = c(stimID,stimID_subj)

    } #blk
    response = response-1
    stimID  =  stimID -1
    a = trials2counts(stimID, response, rating,nRatings, padAmount = 0,padCells=0) # preparing the vectors including frequency of each rate for each response.
    nRp_S1 <- a[[1]]
    nRp_S2 <- a[[2]]
    ns1[,sub]= nRp_S1
    ns2[,sub]= nRp_S2
    
  } #sub
 
  nrg_s1[[dru]]= ns1
  nrg_s2[[dru]]= ns2
  
} #dru

nR_S1 = nrg_s1
nR_S2 = nrg_s2
output <- fit_metad_groupcorr(nR_S1 = nR_S1, nR_S2 = nR_S2) # Fitting to Hmeta, for all three groups considering to correlation between three groups

#saveRDS(output, file= "/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/hmeta_depndent_3group.rds")
```

#The code to check HDI and Rhat (not a main result in the draft)
```{r}
output = readRDS("/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/hmeta_depndent_3group.rds")

Value <- summary(output)
stat <- data.frame(mean = Value$statistics[,"Mean"])
  stat %<>% rownames_to_column(var = "name")
# Rhat 
Value <- gelman.diag(output, confidence = 0.95)
Rhat <- data.frame(conv = Value$psrf)
# HDI 
HDI <- data.frame(HPDinterval(output, prob = 0.95))
HDI %<>%
  rownames_to_column(var = "name")

```

#plot the group posterior distributions for comparison
```{r}
###plot M.Ratio for all three groups
output = readRDS("/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/hmeta_depndent_3group.rds")
mcmcsample <- ggs(output)
mu1 = exp(mcmcsample$value[which(mcmcsample$Parameter=="mu_logMratio[1]")])
mu2 = exp(mcmcsample$value[which(mcmcsample$Parameter=="mu_logMratio[2]")])
mu3 = exp(mcmcsample$value[which(mcmcsample$Parameter=="mu_logMratio[3]")])
effect= cbind(mu1,mu3,mu2)
compare_mbmf_reg_gr_plot(effect)
randcoef = c(mu1,mu3,mu2)
nsam = length(mu1)
drugname = c(rep("Prop",nsam),rep("Plac",nsam),rep("Dop",nsam))
df = data.frame(randcoef ,drugname)
df$drugname = factor(df$drugname,levels = c("Prop","Plac","Dop"))

p =ggplot(df,aes(x = randcoef , fill  = drugname))+
  geom_density(alpha = 0.5)+scale_fill_manual(values=c("#F8766D", "#00BFC4","#619CFF"))+xlab("Meta-cognitive ability")+ylab("Density")+
    labs(title = "")+ xlim(c(0,2))+
    theme_bw( ) + thsara
p
```


#To see the number of samples that are higher in one group relative to another one (not an critical code)
```{r}
### increase by Dopamine and decrease by Prop subject by subject.
output = readRDS("/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/hmeta_depndent_3group.rds")
mcmcsample <- ggs(output)
nsub=30
ndrag = 2
nmethod = 2
ratio_dif_indiv = array(0, c(nsub,ndrag,nmethod)) #prop and Dop minus Place
for (sub in 1:nsub){
    mu1 = mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",1]"))]
    mu2 = mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",2]"))]
    mu3 = mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",3]"))]
    
    
    ratio_dif_indiv[sub,1,1] = length(which(mu1-mu3<0))/length(mu1-mu3)
    ratio_dif_indiv[sub,2,1] = length(which(mu2-mu3>0))/length(mu2-mu3)
    ratio_dif_indiv[sub,1,2] = mean(mu1-mu3)
    ratio_dif_indiv[sub,2,2] = mean(mu2-mu3)
}
# saveRDS(ratio_dif_indiv, file ="/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/mu_deltaM.Ratio_dependentgroups_indiv.rds")

cor.test( ratio_dif_indiv[,1], ratio_dif_indiv[,2])

length(which(mu1-mu3<0))/length(mu1-mu3)
length(which(mu2-mu3>0))/length(mu2-mu3)

```


#plot that compares Hmeta across different groups for each subject.
```{r}
### increase vy Dopamine and decrease by Prop subject by subject.
output = readRDS("/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/hmeta_depndent_3group.rds")
mcmcsample <- ggs(output)
nsub=30
ndrug = 3
meta_indiv = array(0, c(nsub,ndrug)) #prop and Dop minus Place
for (sub in 1:nsub){
    meta_indiv[sub,1] = mean(mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",1]"))]) #prop
    meta_indiv[sub,2] = mean(mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",2]"))]) #dop
    meta_indiv[sub,3] = mean(mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",3]"))]) #plac
    
}
 #saveRDS(meta_indiv, file #="/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/mean_M.Ratio_dependentgroups_indiv.rds")

t.test(meta_indiv[,2],meta_indiv[,3])

p=compare_mbmf_reg_plot(cbind( meta_indiv[,1],meta_indiv[,3],meta_indiv[,2]))
p
```

#Anova test to compare each two groups, individual estimations of Hmeta
```{r}
### Anova to compare individual posteriors from Hmeta, between drug conditions
nsub = 30
tot_2opt = c(meta_indiv[,2],meta_indiv[,3])#,meta_indiv[,3])
drugname = c(rep("pr", nsub), rep("d", nsub))#, rep("pl", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname) )
#aov(tot_2opt~drugname , data = meta) %>% summary() 
kruskal.test(tot_2opt~drugname , data = meta)
```


#compare performance under drugs
```{r}
ndrug = 3
nt_bl =25
nsub = 30
nblk = 8
perf = matrix(0, nrow = ndrug, ncol=nsub) # two is for storring mean and se
rt = matrix(0, nrow = ndrug, ncol=nsub) # two is for storring mean and se
conf = matrix(0, nrow = ndrug, ncol=nsub) # two is for storring mean and se
drug = readRDS("/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/drug.rds")
adressdrug = "/Users/sershadmanesh/Nextcloud/Drug_study/Public/data/main_data/complete/"
completesubs = c(102:112, 114:117, 119:133)  # 4 last added

for (dru in 1:ndrug){
  for(sub in 1:nsub){
    subid = completesubs[sub]
    drugpos = drug[sub,dru]
    data = readMat(paste0(adressdrug,subid,"/","perceptData",subid,"-",drugpos,".mat"))
    perfsub = c()
    rtsub = c()
    confsub = c()
    for (blk in 1:nblk){
      adress_subj = data$DATA[,,blk]$results[,,1]
      perfsub = c(perfsub, adress_subj$correct)
      rtsub = c(rtsub, adress_subj$rt)
      confsub = c(confsub, adress_subj$responseConf)
      
    } #blk
    perf[dru,sub] = mean(perfsub)
    rt[dru,sub] = mean(rtsub)
    conf[dru,sub] = mean(confsub)
  } #sub
} #dru

effectmb= data.frame(perf[1,],perf[3,],perf[2,])
p2 = compare_mbmf_reg_plot(effectmb)
p2
ggsave("/Users/sershadmanesh/Nextcloud/Drug_study/Public/images/perfperc_drugs.jpeg",p2,width = 8,height = 8,units = "cm")


#Anova  
  allcoef = c(perf[1,],perf[3,],perf[2,])#confcor_med
  drugname = c(rep("p",nsub),rep("pl",nsub),rep("d",nsub))
  subs = rep(c(1:nsub), 3)
  meta = data.frame(allcoef,drugname = as.factor(drugname), subs)
  resaov = aov(allcoef~drugname+(1/subs) , data = meta)
  summary(resaov)
  
```
